---
title: "Exit Survey Results"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE}
library(data.table)
library(tidyverse)
library(kableExtra)
library(formattable)
```

```{r include=FALSE}
source('./data_funs.R')
```

```{r include=FALSE}

exit_raw <- fread("./raw_data/raw_data_DSSG_2019___Exit_Survey2019_09_12_19_06_57.csv")
```

## Prior to DSSG, what was your experiance with programming?

```{r echo=F}

prior <- exit_raw %>%
  select(3:7)

col_nam <- names(prior)

colnames(prior) <- trimws(tstrsplit(col_nam, ">>")[[2]])

keycol <- "question"
valuecol <- "value"
gathercols <- c("I had never done any programming", "I had programmed but not in the context of my work/research",
"I used programming minimally in my work/research", "I used programming moderately in my work/research",          
"I used programming extensively in my work/research") 

prior_t <- prior %>%
gather_(., keycol, valuecol, gathercols) %>%
  group_by(question, value) %>%
  summarise(n = n()) %>%
  filter(value == 'Select one') %>%
  ungroup() %>%
  select(-value) %>%
  mutate(per = round(n/sum(n)*100, 1))  

#kable(prior_t) %>%
#  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
#                footnote(general = " % values are percents." )

prior_t %>% arrange(-n) %>%
  mutate(percent = color_bar("#bcbddc")(per)) %>%
  select(-per) %>%
  kable("html", escape = F) %>%
  kable_styling("hover", full_width = F) %>%
  column_spec(3, width = "4cm")

```

## Please indicate programming experience in the following languages
```{r include=FALSE}
prog_ex <- exit_raw %>%
  select(8:16)

col_nam <- names(prog_ex)

colnames(prog_ex) <- trimws(tstrsplit(col_nam, ">>")[[2]])

keycol <- "Languages"
valuecol <- "value"
gathercols <- c("Python", "R", "Matlab", "Julia", "SQL",
                "Java", "Stata/SAS", "Shell scripting, e.g. bash", "Other") 

prog_ex_t <- prog_ex  %>%
gather_(., keycol, valuecol, gathercols) %>%
  group_by(Languages, value) %>%
  summarise(n = n()) %>%
  mutate(value = gsub(pattern = "<.*>", replacement = "", value),
         perc = round(n/sum(n)*100))
```

```{r echo = FALSE}

prior_dssg <- prog_ex_t %>%
  filter(value == "Prior to the DSSG") %>%
  select(-value) %>% data.frame()

after_dssg <- prog_ex_t %>%
  filter(value == "Now") %>%
  select(-value) %>% data.frame()

# unit.scale = function(x) (x - min(x)) / (max(x) - min(x))
prior_dssg  %>%  arrange(-n) %>%
  mutate(percent = formattable::color_bar("#9ecae1")(perc)) %>%
  select(-perc) %>%
  kable("html", escape = F) %>%
  kable_styling("hover", full_width = F) %>%
  column_spec(3, width = "4cm") %>%
  add_header_above(c("Prior to DSSG...", "", "")) %>%
  footnote(general = "Assumption: 12 Total Respondents per language." )

# unit.scale = function(x) (x - min(x)) / (max(x) - min(x))
```

```{r echo = FALSE}
after_dssg <- prog_ex_t %>%
  filter(value == "Now") %>%
  select(-value) %>% data.frame()

after_dssg  %>%  arrange(-n) %>%
  mutate(percent = formattable::color_bar("#a1d99b")(perc)) %>%
  select(-perc) %>%
  kable("html", escape = F) %>%
  kable_styling("hover", full_width = F) %>%
  column_spec(3, width = "4cm") %>%
  add_header_above(c("Now...", "", "")) %>%
  footnote(general = "Assumption: 12 Total Respondents per language." )
```

## Prior to DSSG were you familiar with Git version control?

```{r echo = FALSE}
git_v <- exit_raw %>%
  select(20:21)

col_nam <- names(git_v)

colnames(git_v) <- trimws(tstrsplit(col_nam, ">>")[[2]])

keycol <- "Prior familiarity"
valuecol <- "value"
gathercols <- c("Yes", "No") 

git_v_t <- git_v  %>%
gather_(., keycol, valuecol, gathercols) %>%
  group_by(`Prior familiarity`, value) %>%
  summarise(n = n()) %>%
  mutate(perc = round(n/sum(n)*100)) %>%
  filter(value == "Select one") %>% data.table()

git_v_t  %>%  arrange(-n) %>%
  mutate(percent = formattable::color_bar("#7fcdbb")(perc)) %>%
  select(-perc, -value) %>%
  kable("html", escape = F) %>%
  kable_styling("hover", full_width = F) %>%
  column_spec(3, width = "5cm") %>%
  add_header_above(c("", "", "")) %>%
  footnote(general = "12 Total Respondents" )
```

## After the DSSG, could you, given the URL for a project on GitHub, check out a working copy of that project, add a file called notes.txt, and commit the change?

```{r echo = FALSE}
git_v <- exit_raw %>%
  select(22:23)

col_nam <- names(git_v)

colnames(git_v) <- trimws(tstrsplit(col_nam, ">>")[[2]])

keycol <- "Can you do this?"
valuecol <- "value"
gathercols <- c("Yes", "No") 

git_v_t <- git_v  %>%
gather_(., keycol, valuecol, gathercols) %>%
  group_by(`Can you do this?`, value) %>%
  summarise(n = n()) %>%
  mutate(perc = round(n/sum(n)*100)) %>%
  filter(value == "Select one") %>% data.table()

git_v_t  %>%  arrange(-n) %>%
  mutate(percent = formattable::color_bar("#fa9fb5")(perc)) %>%
  select(-perc, -value) %>%
  kable("html", escape = F) %>%
  kable_styling("hover", full_width = F) %>%
  column_spec(3, width = "5cm") %>%
  add_header_above(c("", "", "")) %>%
  footnote(general = "12 Total Respondents" )
```


```{r echo = FALSE}
value_dssg <- exit_raw %>%
  select(24:40)

col_nam <- names(value_dssg)

colnames(value_dssg) <- trimws(tstrsplit(col_nam, ">>")[[2]])

value_dssg <- value_dssg %>%
  mutate_all(as.character)

data_list <- data_mung(value_dssg, 1, 17)

df_plot = do.call(bind_rows, data_list) %>%
  select(question, `-2_perc`, `-1_perc`,`0_perc`,`1_perc`, `2_perc`)

df_melted <- likert_df(df_plot, id = "question")

highs<-df_melted[35:85,] %>%
  na.omit()
lows<-df_melted[1:34,] %>%
  na.omit()

highs <- highs[rev(rownames(highs)),] 
```

## What components of the DSSG program did you find most and least valuable? Please score each of the following on a scale of -2 to 2, where -2 indicate a negative impact on your experience and 2 indicates a positive impact.

```{r, echo=FALSE, fig.height=14}
levels<-c("-2", "-1", "0",  "1", "2")

plot_fun(highs,lows, mylevels = levels, divergent = T)
```






