---
title: "Tutotial Feedback"
output: html_document
---

```{r include=FALSE}
library(data.table)
library(tidyverse)
library(kableExtra)
source('./data_funs.R')
```

# Tutorial Feedback Outcomes


### Some informative text.

```{r setup, include=FALSE}
file_nms <- list.files("./raw_data/", pattern="*.csv$")

# load workshop feed back files 
tutorial_fms = intersect(list.files("./raw_data/", pattern="Tutorial"), 
                 list.files("./raw_data/", pattern="*.csv$"))

temp <- lapply(file.path("./raw_data" ,tutorial_fms), fread, stringsAsFactors = FALSE, skip=1,header =T)

tutorial_fms

# check number of columns 
for(i in 1:17) {
print(dim(temp[[i]])[2])

}

# varying columns = surveys not consisntent across topics 
```

# Building Web Applications in Python 

```{r include=FALSE}
data_temp <- temp[[1]]
names(data_temp)

cols_lev_a <- names(table(data_temp[,4]))
cols_lev_b <- 'No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'
cols_lev_c <- union(names(table(data_temp[,11])),names(table(data_temp[,12])))

```

```{r,  include=F}
# looking at the likert questions 4:8
data_list <- data_mung(df = data_temp,
  r1 = 4,
  r2 = 12)
```

```{r, include=F}
results_all <- do.call(bind_rows, data_list) 
names(results_all)
results <-  results_all %>%
  select(question,
         matches(paste0(cols_lev_a,'_perc' ,collapse="|")),
         matches(cols_lev_b),
         matches(paste0(cols_lev_c,'_perc' ,collapse="|"))) %>%
  mutate(`Q's` = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6','Q7', 'Q8', 'Q9'))
```

```{r, echo=FALSE}
table1 <- results %>%
  select(`Q's`, `survey item`=question)

kable(table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)


```

```{r include=F}
length(cols_lev_a)
```

```{r, echo=FALSE}
table_q1 <- results %>%
  filter(`Q's` == 'Q1') %>%
  select(`Q's`, matches('1=Not at all familiar_perc|2=A little familiar_perc|3=Moderately familiar_perc|4=Very familiar_perc|5=Extremely familiar')) %>%
  select(`Q's`,noquote(order(colnames(.))))  

kable(table_q1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = " % values are percents." )
```

```{r echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, echo=FALSE}
table_q2 <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`,matches('No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'))

kable(table_q2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

```{r fig.height=8, echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r include=F}
length(cols_lev_c)
```

```{r fig.height=8, echo=FALSE}
table_q3 <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, matches('0=Not applicable_perc|1=Not at all_perc|2=Slightly_perc|3=Moderately_perc|4=Considerably_perc|5=Completely_perc')) %>%
  select(`Q's`,noquote(order(colnames(.))))

kable(table_q3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

# Data Analysis with Jupyter, GeoPandas and SQL

```{r include=FALSE}
data_temp <- temp[[2]]
names(data_temp)

cols_lev_a <- names(table(data_temp[,4]))
cols_lev_b <- 'No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'
cols_lev_c <- union(names(table(data_temp[,11])),names(table(data_temp[,12])))

```

```{r,  include=F}
# looking at the likert questions 4:8
data_list <- data_mung(df = data_temp,
  r1 = 4,
  r2 = 12)
```

```{r, include=F}
results_all <- do.call(bind_rows, data_list) 
names(results_all)
results <-  results_all %>%
  select(question,
         matches(paste0(cols_lev_a,'_perc' ,collapse="|")),
         matches(cols_lev_b),
         matches(paste0(cols_lev_c,'_perc' ,collapse="|"))) %>%
  mutate(`Q's` = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6','Q7', 'Q8', 'Q9'))
```

```{r, echo=FALSE}
table1 <- results %>%
  select(`Q's`, `survey item`=question)

kable(table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)


```

```{r include=F}
length(cols_lev_a)
```

```{r, echo=FALSE}
table_q1 <- results %>%
  filter(`Q's` == 'Q1') %>%
  select(`Q's`, matches('1=Not at all familiar_perc|2=A little familiar_perc|3=Moderately familiar_perc|4=Very familiar_perc|5=Extremely familiar')) %>%
  select(`Q's`,noquote(order(colnames(.))))  

kable(table_q1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = " % values are percents." )
```

```{r echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, echo=FALSE}
table_q2 <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`,matches('No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'))

kable(table_q2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

```{r fig.height=8, echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r include=F}
length(cols_lev_c)
```

```{r fig.height=8, echo=FALSE}
table_q3 <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, matches('0=Not applicable_perc|1=Not at all_perc|2=Slightly_perc|3=Moderately_perc|4=Considerably_perc|5=Completely_perc')) %>%
  select(`Q's`,noquote(order(colnames(.))))

kable(table_q3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

# Git and Git Workflow

```{r include=FALSE}
data_temp <- temp[[3]]
names(data_temp)

cols_lev_a <- names(table(data_temp[,4]))
cols_lev_b <- 'No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'
cols_lev_c <- union(names(table(data_temp[,11])),names(table(data_temp[,12])))

```

```{r,  include=F}
# looking at the likert questions 4:8
data_list <- data_mung(df = data_temp,
  r1 = 4,
  r2 = 12)
```

```{r, include=F}
results_all <- do.call(bind_rows, data_list) 
names(results_all)
results <-  results_all %>%
  select(question,
         matches(paste0(cols_lev_a,'_perc' ,collapse="|")),
         matches(cols_lev_b),
         matches(paste0(cols_lev_c,'_perc' ,collapse="|"))) %>%
  mutate(`Q's` = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6','Q7', 'Q8', 'Q9'))
```

```{r, echo=FALSE}
table1 <- results %>%
  select(`Q's`, `survey item`=question)

kable(table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)


```

```{r include=F}
length(cols_lev_a)
```

```{r, echo=FALSE}
table_q1 <- results %>%
  filter(`Q's` == 'Q1') %>%
  select(`Q's`, matches('1=Not at all familiar_perc|2=A little familiar_perc|3=Moderately familiar_perc|4=Very familiar_perc|5=Extremely familiar')) %>%
  select(`Q's`,noquote(order(colnames(.))))  

kable(table_q1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = " % values are percents." )
```

```{r echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, echo=FALSE}
table_q2 <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`,matches('No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'))

kable(table_q2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

```{r fig.height=8, echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r include=F}
length(cols_lev_c)
```

```{r fig.height=8, echo=FALSE}
table_q3 <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, matches('0=Not applicable_perc|1=Not at all_perc|2=Slightly_perc|3=Moderately_perc|4=Considerably_perc|5=Completely_perc')) %>%
  select(`Q's`,noquote(order(colnames(.))))

kable(table_q3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

# Git and GitHub
 
```{r include=FALSE}
data_temp <- temp[[4]]
names(data_temp)

cols_lev_a <- names(table(data_temp[,4]))
cols_lev_b <- 'No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'
cols_lev_c <- union(names(table(data_temp[,11])),names(table(data_temp[,12])))

```

```{r,  include=F}
# looking at the likert questions 4:8
data_list <- data_mung(df = data_temp,
  r1 = 4,
  r2 = 12)
```

```{r, include=F}
results_all <- do.call(bind_rows, data_list) 
names(results_all)
results <-  results_all %>%
  select(question,
         matches(paste0(cols_lev_a,'_perc' ,collapse="|")),
         matches(cols_lev_b),
         matches(paste0(cols_lev_c,'_perc' ,collapse="|"))) %>%
  mutate(`Q's` = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6','Q7', 'Q8', 'Q9'))
```

```{r, echo=FALSE}
table1 <- results %>%
  select(`Q's`, `survey item`=question)

kable(table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)


```

```{r include=F}
length(cols_lev_a)
```

```{r, echo=FALSE}
table_q1 <- results %>%
  filter(`Q's` == 'Q1') %>%
  select(`Q's`, matches('1=Not at all familiar_perc|2=A little familiar_perc|3=Moderately familiar_perc|4=Very familiar_perc|5=Extremely familiar')) %>%
  select(`Q's`,noquote(order(colnames(.))))  

kable(table_q1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = " % values are percents." )
```

```{r echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, echo=FALSE}
table_q2 <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`,matches('No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'))

kable(table_q2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

```{r fig.height=8, echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r include=F}
length(cols_lev_c)
```

```{r fig.height=8, echo=FALSE}
table_q3 <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, matches('0=Not applicable_perc|1=Not at all_perc|2=Slightly_perc|3=Moderately_perc|4=Considerably_perc|5=Completely_perc')) %>%
  select(`Q's`,noquote(order(colnames(.))))

kable(table_q3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```
 
# High Performance Python
 
```{r include=FALSE}
high_py <- temp[[5]]
names(high_py)

cols_lev_a <- names(table(high_py[,4]))
cols_lev_b <- 'No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'
cols_lev_c <- union(names(table(high_py[,11])),names(table(high_py[,12])))

```

```{r,  include=F}
# looking at the likert questions 4:8
data_list <- data_mung(df = high_py,
  r1 = 4,
  r2 = 12)
```

```{r, include=F}
results_all <- do.call(bind_rows, data_list) 
names(results_all)
results <-  results_all %>%
  select(question,
         matches(paste0(cols_lev_a,'_perc' ,collapse="|")),
         matches(cols_lev_b),
         matches(paste0(cols_lev_c,'_perc' ,collapse="|"))) %>%
  mutate(`Q's` = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6','Q7', 'Q8', 'Q9'))
```

```{r, echo=FALSE}
table1 <- results %>%
  select(`Q's`, `survey item`=question)

kable(table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)


```

```{r include=F}
length(cols_lev_a)
```

```{r, echo=FALSE}
table_q1 <- results %>%
  filter(`Q's` == 'Q1') %>%
  select(`Q's`, `1=Not at all familiar_perc`,`2=A little familiar_perc`, `3=Moderately familiar_perc`)

kable(table_q1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = " % values are percents." )
```

```{r echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, echo=FALSE}
table_q2 <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`, matches('No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'))

kable(table_q2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

```{r fig.height=8, echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r include=F}
length(cols_lev_c)
```

```{r fig.height=8, echo=FALSE}
table_q3 <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, `1=Not at all_perc`, `2=Slightly_perc`, `3=Moderately_perc`, `4=Considerably_perc`, `5=Completely_perc`)

kable(table_q3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```
 
# Intro to Tableau
 
```{r include=FALSE}
int_tab <- temp[[6]]
names(int_tab)

cols_lev_a <- names(table(int_tab[,4]))
cols_lev_b <- 'No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'
cols_lev_c <- union(names(table(int_tab[,11])),names(table(int_tab[,12])))

```

```{r,  include=F}
# looking at the likert questions 4:8
data_list <- data_mung(df = int_tab,
  r1 = 4,
  r2 = 12)
```

```{r, include=F}
results_all <- do.call(bind_rows, data_list) 
names(results_all)
results <-  results_all %>%
  select(question,
         matches(paste0(cols_lev_a,'_perc' ,collapse="|")),
         matches(cols_lev_b),
         matches(paste0(cols_lev_c,'_perc' ,collapse="|"))) %>%
  mutate(`Q's` = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6','Q7', 'Q8', 'Q9'))
```

```{r, echo=FALSE}
table1 <- results %>%
  select(`Q's`, `survey item`=question)

kable(table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)


```

```{r include=F}
length(cols_lev_a)
```

```{r, echo=FALSE}
table_q1 <- results %>%
  filter(`Q's` == 'Q1') %>%
  select(`Q's`, matches('1=Not at all familiar_perc|2=A little familiar_perc|3=Moderately familiar_perc|4=Very familiar_perc|5=Extremely familiar')) %>%
  select(`Q's`,noquote(order(colnames(.))))  

kable(table_q1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = " % values are percents." )
```

```{r echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, echo=FALSE}
table_q2 <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`,matches('No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'))

kable(table_q2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

```{r fig.height=8, echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r include=F}
length(cols_lev_c)
```

```{r fig.height=8, echo=FALSE}
table_q3 <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, matches('0=Not applicable_perc|1=Not at all_perc|2=Slightly_perc|3=Moderately_perc|4=Considerably_perc|5=Completely_perc')) %>%
  select(`Q's`,noquote(order(colnames(.))))

kable(table_q3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```
 
# Introduction to Visual Communication

```{r include=FALSE}
data_temp <- temp[[7]]
names(data_temp)

cols_lev_a <- names(table(data_temp[,4]))
cols_lev_b <- 'No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'
cols_lev_c <- union(names(table(data_temp[,11])),names(table(data_temp[,12])))

```

```{r,  include=F}
# looking at the likert questions 4:8
data_list <- data_mung(df = data_temp,
  r1 = 4,
  r2 = 12)
```

```{r, include=F}
results_all <- do.call(bind_rows, data_list) 
names(results_all)
results <-  results_all %>%
  select(question,
         matches(paste0(cols_lev_a,'_perc' ,collapse="|")),
         matches(cols_lev_b),
         matches(paste0(cols_lev_c,'_perc' ,collapse="|"))) %>%
  mutate(`Q's` = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6','Q7', 'Q8', 'Q9'))
```

```{r, echo=FALSE}
table1 <- results %>%
  select(`Q's`, `survey item`=question)

kable(table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)


```

```{r include=F}
length(cols_lev_a)
```

```{r, echo=FALSE}
table_q1 <- results %>%
  filter(`Q's` == 'Q1') %>%
  select(`Q's`, matches('1=Not at all familiar_perc|2=A little familiar_perc|3=Moderately familiar_perc|4=Very familiar_perc|5=Extremely familiar')) %>%
  select(`Q's`,noquote(order(colnames(.))))  

kable(table_q1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = " % values are percents." )
```

```{r echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, echo=FALSE}
table_q2 <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`,matches('No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'))

kable(table_q2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

```{r fig.height=8, echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r include=F}
length(cols_lev_c)
```

```{r fig.height=8, echo=FALSE}
table_q3 <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, matches('0=Not applicable_perc|1=Not at all_perc|2=Slightly_perc|3=Moderately_perc|4=Considerably_perc|5=Completely_perc')) %>%
  select(`Q's`,noquote(order(colnames(.))))

kable(table_q3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```
 
# Machine Learning with Scikit Learn

```{r include=FALSE}
data_temp <- temp[[8]]
names(data_temp)

cols_lev_a <- names(table(data_temp[,4]))
cols_lev_b <- 'No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'
cols_lev_c <- union(names(table(data_temp[,11])),names(table(data_temp[,12])))

```

```{r,  include=F}
# looking at the likert questions 4:8
data_list <- data_mung(df = data_temp,
  r1 = 4,
  r2 = 12)
```

```{r, include=F}
results_all <- do.call(bind_rows, data_list) 
names(results_all)
results <-  results_all %>%
  select(question,
         matches(paste0(cols_lev_a,'_perc' ,collapse="|")),
         matches(cols_lev_b),
         matches(paste0(cols_lev_c,'_perc' ,collapse="|"))) %>%
  mutate(`Q's` = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6','Q7', 'Q8', 'Q9'))
```

```{r, echo=FALSE}
table1 <- results %>%
  select(`Q's`, `survey item`=question)

kable(table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)


```

```{r include=F}
length(cols_lev_a)
```

```{r, echo=FALSE}
table_q1 <- results %>%
  filter(`Q's` == 'Q1') %>%
  select(`Q's`, matches('1=Not at all familiar_perc|2=A little familiar_perc|3=Moderately familiar_perc|4=Very familiar_perc|5=Extremely familiar')) %>%
  select(`Q's`,noquote(order(colnames(.))))  

kable(table_q1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = " % values are percents." )
```

```{r echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, echo=FALSE}
table_q2 <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`,matches('No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'))

kable(table_q2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

```{r fig.height=8, echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r include=F}
length(cols_lev_c)
```

```{r fig.height=8, echo=FALSE}
table_q3 <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, matches('0=Not applicable_perc|1=Not at all_perc|2=Slightly_perc|3=Moderately_perc|4=Considerably_perc|5=Completely_perc')) %>%
  select(`Q's`,noquote(order(colnames(.))))

kable(table_q3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```
 
 # Object Oriented Programming 

```{r include=FALSE}
data_temp <- temp[[9]]
names(data_temp)

cols_lev_a <- names(table(data_temp[,4]))
cols_lev_b <- 'No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'
cols_lev_c <- union(names(table(data_temp[,11])),names(table(data_temp[,12])))
```

```{r,  include=F}
# looking at the likert questions 4:8
data_list <- data_mung(df = data_temp,
  r1 = 4,
  r2 = 12)
```

```{r, include=F}
results_all <- do.call(bind_rows, data_list) 
names(results_all)
results <-  results_all %>%
  select(question,
         matches(paste0(cols_lev_a,'_perc' ,collapse="|")),
         matches(cols_lev_b),
         matches(paste0(cols_lev_c,'_perc' ,collapse="|"))) %>%
  mutate(`Q's` = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6','Q7', 'Q8', 'Q9'))
```

```{r, echo=FALSE}
table1 <- results %>%
  select(`Q's`, `survey item`=question)

kable(table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)


```

```{r include=F}
length(cols_lev_a)
```

```{r, echo=FALSE}
table_q1 <- results %>%
  filter(`Q's` == 'Q1') %>%
  select(`Q's`, matches('1=Not at all familiar_perc|2=A little familiar_perc|3=Moderately familiar_perc|4=Very familiar_perc|5=Extremely familiar')) %>%
  select(`Q's`,noquote(order(colnames(.))))  

kable(table_q1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = " % values are percents." )
```

```{r echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, echo=FALSE}
table_q2 <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`,matches('No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'))

kable(table_q2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

```{r fig.height=8, echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r include=F}
length(cols_lev_c)
```

```{r fig.height=8, echo=FALSE}
table_q3 <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, matches('0=Not applicable_perc|1=Not at all_perc|2=Slightly_perc|3=Moderately_perc|4=Considerably_perc|5=Completely_perc')) %>%
  select(`Q's`,noquote(order(colnames(.))))

kable(table_q3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```
 
 # Pair Programming 

```{r include=FALSE}
data_temp <- temp[[10]]
names(data_temp)

cols_lev_a <- names(table(data_temp[,4]))
cols_lev_b <- 'No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'
cols_lev_c <- union(names(table(data_temp[,11])),names(table(data_temp[,12])))

```

```{r,  include=F}
# looking at the likert questions 4:8
data_list <- data_mung(df = data_temp,
  r1 = 4,
  r2 = 12)
```

```{r, include=F}
results_all <- do.call(bind_rows, data_list) 
names(results_all)
results <-  results_all %>%
  select(question,
         matches(paste0(cols_lev_a,'_perc' ,collapse="|")),
         matches(cols_lev_b),
         matches(paste0(cols_lev_c,'_perc' ,collapse="|"))) %>%
  mutate(`Q's` = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6','Q7', 'Q8', 'Q9'))
```

```{r, echo=FALSE}
table1 <- results %>%
  select(`Q's`, `survey item`=question)

kable(table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)


```

```{r include=F}
length(cols_lev_a)
```

```{r, echo=FALSE}
table_q1 <- results %>%
  filter(`Q's` == 'Q1') %>%
  select(`Q's`, matches('1=Not at all familiar_perc|2=A little familiar_perc|3=Moderately familiar_perc|4=Very familiar_perc|5=Extremely familiar')) %>%
  select(`Q's`,noquote(order(colnames(.))))  

kable(table_q1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = " % values are percents." )
```

```{r echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, echo=FALSE}
table_q2 <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`,matches('No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'))

kable(table_q2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

```{r fig.height=8, echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r include=F}
length(cols_lev_c)
```

```{r fig.height=8, echo=FALSE}
table_q3 <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, matches('0=Not applicable_perc|1=Not at all_perc|2=Slightly_perc|3=Moderately_perc|4=Considerably_perc|5=Completely_perc')) %>%
  select(`Q's`,noquote(order(colnames(.))))

kable(table_q3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```
 
 # Project Organization, Virtualization, and Continuous Intergration 

```{r include=FALSE}
data_temp <- temp[[11]]
names(data_temp)

cols_lev_a <- names(table(data_temp[,4]))
cols_lev_b <- 'No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'
cols_lev_c <- union(names(table(data_temp[,11])),names(table(data_temp[,12])))

```

```{r,  include=F}
# looking at the likert questions 4:8
data_list <- data_mung(df = data_temp ,
  r1 = 4,
  r2 = 12)
```

```{r, include=F}
results_all <- do.call(bind_rows, data_list) 
names(results_all)
results <-  results_all %>%
  select(question,
         matches(paste0(cols_lev_a,'_perc' ,collapse="|")),
         matches(cols_lev_b),
         matches(paste0(cols_lev_c,'_perc' ,collapse="|"))) %>%
  mutate(`Q's` = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6','Q7', 'Q8', 'Q9'))
```

```{r, echo=FALSE}
table1 <- results %>%
  select(`Q's`, `survey item`=question)

kable(table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)


```

```{r include=F}
length(cols_lev_a)
```

```{r, echo=FALSE}
table_q1 <- results %>%
  filter(`Q's` == 'Q1') %>%
  select(`Q's`, matches('1=Not at all familiar_perc|2=A little familiar_perc|3=Moderately familiar_perc|4=Very familiar_perc|5=Extremely familiar')) %>%
  select(`Q's`,noquote(order(colnames(.))))  

kable(table_q1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = " % values are percents." )
```

```{r echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, echo=FALSE}
table_q2 <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`,matches('No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'))

kable(table_q2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

```{r fig.height=8, echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r include=F}
length(cols_lev_c)
```

```{r fig.height=8, echo=FALSE}
table_q3 <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, matches('0=Not applicable_perc|1=Not at all_perc|2=Slightly_perc|3=Moderately_perc|4=Considerably_perc|5=Completely_perc')) %>%
  select(`Q's`,noquote(order(colnames(.))))

kable(table_q3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```
 
 # Public Speaking 

```{r include=FALSE}
data_temp <- temp[[12]]
names(data_temp)

cols_lev_a <- names(table(data_temp[,4]))
cols_lev_b <- 'No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'
cols_lev_c <- union(names(table(data_temp[,11])),names(table(data_temp[,12])))

```

```{r,  include=F}
# looking at the likert questions 4:8
data_list <- data_mung(df = data_temp,
  r1 = 4,
  r2 = 12)
```

```{r, include=F}
results_all <- do.call(bind_rows, data_list) 
names(results_all)
results <-  results_all %>%
  select(question,
         matches(paste0(cols_lev_a,'_perc' ,collapse="|")),
         matches(cols_lev_b),
         matches(paste0(cols_lev_c,'_perc' ,collapse="|"))) %>%
  mutate(`Q's` = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6','Q7', 'Q8', 'Q9'))
```

```{r, echo=FALSE}
table1 <- results %>%
  select(`Q's`, `survey item`=question)

kable(table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)


```

```{r include=F}
length(cols_lev_a)
```

```{r, echo=FALSE}
table_q1 <- results %>%
  filter(`Q's` == 'Q1') %>%
  select(`Q's`, matches('1=Not at all familiar_perc|2=A little familiar_perc|3=Moderately familiar_perc|4=Very familiar_perc|5=Extremely familiar')) %>%
  select(`Q's`,noquote(order(colnames(.))))  

kable(table_q1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = " % values are percents." )
```

```{r echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, echo=FALSE}
table_q2 <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`,matches('No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'))

kable(table_q2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

```{r fig.height=8, echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r include=F}
length(cols_lev_c)
```

```{r fig.height=8, echo=FALSE}
table_q3 <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, matches('0=Not applicable_perc|1=Not at all_perc|2=Slightly_perc|3=Moderately_perc|4=Considerably_perc|5=Completely_perc')) %>%
  select(`Q's`,noquote(order(colnames(.))))

kable(table_q3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

 # Python Coding Standards and Documentation 
```{r include=FALSE}
data_temp <- temp[[13]]
names(data_temp)

cols_lev_a <- names(table(data_temp[,4]))
cols_lev_b <- 'No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'
cols_lev_c <- union(names(table(data_temp[,10])),names(table(data_temp[,11])))

```

```{r,  include=F}
# looking at the likert questions 4:8
data_list <- data_mung(df = data_temp,
  r1 = 4,
  r2 = 11)
```

```{r, include=F}
results_all <- do.call(bind_rows, data_list) 
names(results_all)
results <-  results_all %>%
  select(question,
         matches(paste0(cols_lev_a,'_perc' ,collapse="|")),
         matches(cols_lev_b),
         matches(paste0(cols_lev_c,'_perc' ,collapse="|"))) %>%
  mutate(`Q's` = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6','Q7', 'Q8'))
```

```{r, echo=FALSE}
table1 <- results %>%
  select(`Q's`, `survey item`=question)

kable(table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)


```

```{r include=F}
length(cols_lev_a)
```

```{r, echo=FALSE}
table_q1 <- results %>%
  filter(`Q's` == 'Q1') %>%
  select(`Q's`, matches('1=Not at all familiar_perc|2=A little familiar_perc|3=Moderately familiar_perc|4=Very familiar_perc|5=Extremely familiar')) %>%
  select(`Q's`,noquote(order(colnames(.))))  

kable(table_q1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = " % values are percents." )
```

```{r echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, echo=FALSE}
table_q2 <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6')) %>%
  select(`Q's`,matches('No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'))

kable(table_q2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

```{r fig.height=8, echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q7','Q8')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r include=F}
length(cols_lev_c)
```

```{r fig.height=8, echo=FALSE}
table_q3 <- results %>%
  filter(`Q's` %in% c('Q7','Q8')) %>%
  select(`Q's`, matches('0=Not applicable_perc|1=Not at all_perc|2=Slightly_perc|3=Moderately_perc|4=Considerably_perc|5=Completely_perc')) %>%
  select(`Q's`,noquote(order(colnames(.))))

kable(table_q3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```
 
 # Software Design
 
```{r include=FALSE}
data_temp <- temp[[14]]
names(data_temp)

cols_lev_a <- names(table(data_temp[,4]))
cols_lev_b <- 'No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'
cols_lev_c <- union(names(table(data_temp[,11])),names(table(data_temp[,12])))

```

```{r,  include=F}
# looking at the likert questions 4:8
data_list <- data_mung(df = data_temp,
  r1 = 4,
  r2 = 12)
```

```{r, include=F}
results_all <- do.call(bind_rows, data_list) 
names(results_all)
results <-  results_all %>%
  select(question,
         matches(paste0(cols_lev_a,'_perc' ,collapse="|")),
         matches(cols_lev_b),
         matches(paste0(cols_lev_c,'_perc' ,collapse="|"))) %>%
  mutate(`Q's` = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6','Q7', 'Q8', 'Q9'))
```

```{r, echo=FALSE}
table1 <- results %>%
  select(`Q's`, `survey item`=question)

kable(table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)


```

```{r include=F}
length(cols_lev_a)
```

```{r, echo=FALSE}
table_q1 <- results %>%
  filter(`Q's` == 'Q1') %>%
  select(`Q's`, matches('1=Not at all familiar_perc|2=A little familiar_perc|3=Moderately familiar_perc|4=Very familiar_perc|5=Extremely familiar')) %>%
  select(`Q's`,noquote(order(colnames(.))))  

kable(table_q1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = " % values are percents." )
```

```{r echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, echo=FALSE}
table_q2 <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`,matches('No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'))

kable(table_q2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

```{r fig.height=8, echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r include=F}
length(cols_lev_c)
```

```{r fig.height=8, echo=FALSE}
table_q3 <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, matches('0=Not applicable_perc|1=Not at all_perc|2=Slightly_perc|3=Moderately_perc|4=Considerably_perc|5=Completely_perc')) %>%
  select(`Q's`,noquote(order(colnames(.))))

kable(table_q3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```
 
 # Team Management Processes 

```{r include=FALSE}
data_temp <- temp[[15]]
names(data_temp)

cols_lev_a <- names(table(data_temp[,4]))
cols_lev_b <- 'No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'
cols_lev_c <- union(names(table(data_temp[,11])),names(table(data_temp[,12])))

```

```{r,  include=F}
# looking at the likert questions 4:8
data_list <- data_mung(df = data_temp,
  r1 = 4,
  r2 = 12)
```

```{r, include=F}
results_all <- do.call(bind_rows, data_list) 
names(results_all)
results <-  results_all %>%
  select(question,
         matches(paste0(cols_lev_a,'_perc' ,collapse="|")),
         matches(cols_lev_b),
         matches(paste0(cols_lev_c,'_perc' ,collapse="|"))) %>%
  mutate(`Q's` = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6','Q7', 'Q8', 'Q9'))
```

```{r, echo=FALSE}
table1 <- results %>%
  select(`Q's`, `survey item`=question)

kable(table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)


```

```{r include=F}
length(cols_lev_a)
```

```{r, echo=FALSE}
table_q1 <- results %>%
  filter(`Q's` == 'Q1') %>%
  select(`Q's`, matches('1=Not at all familiar_perc|2=A little familiar_perc|3=Moderately familiar_perc|4=Very familiar_perc|5=Extremely familiar')) %>%
  select(`Q's`,noquote(order(colnames(.))))  

kable(table_q1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = " % values are percents." )
```

```{r echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, echo=FALSE}
table_q2 <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`,matches('No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'))

kable(table_q2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

```{r fig.height=8, echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r include=F}
length(cols_lev_c)
```

```{r fig.height=8, echo=FALSE}
table_q3 <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, matches('0=Not applicable_perc|1=Not at all_perc|2=Slightly_perc|3=Moderately_perc|4=Considerably_perc|5=Completely_perc')) %>%
  select(`Q's`,noquote(order(colnames(.))))

kable(table_q3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

 # Unit Testing 
 
```{r include=FALSE}
data_temp <- temp[[16]]
names(data_temp)

cols_lev_a <- names(table(data_temp[,4]))
cols_lev_b <- 'No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'
cols_lev_c <- union(names(table(data_temp[,11])),names(table(data_temp[,12])))

```

```{r,  include=F}
# looking at the likert questions 4:8
data_list <- data_mung(df = data_temp,
  r1 = 4,
  r2 = 12)
```

```{r, include=F}
results_all <- do.call(bind_rows, data_list) 
names(results_all)
results <-  results_all %>%
  select(question,
         matches(paste0(cols_lev_a,'_perc' ,collapse="|")),
         matches(cols_lev_b),
         matches(paste0(cols_lev_c,'_perc' ,collapse="|"))) %>%
  mutate(`Q's` = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6','Q7', 'Q8', 'Q9'))
```

```{r, echo=FALSE}
table1 <- results %>%
  select(`Q's`, `survey item`=question)

kable(table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)


```

```{r include=F}
length(cols_lev_a)
```

```{r, echo=FALSE}
table_q1 <- results %>%
  filter(`Q's` == 'Q1') %>%
  select(`Q's`, matches('1=Not at all familiar_perc|2=A little familiar_perc|3=Moderately familiar_perc|4=Very familiar_perc|5=Extremely familiar')) %>%
  select(`Q's`,noquote(order(colnames(.))))  

kable(table_q1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = " % values are percents." )
```

```{r echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, echo=FALSE}
table_q2 <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6', 'Q7')) %>%
  select(`Q's`,matches('No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'))

kable(table_q2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

```{r fig.height=8, echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r include=F}
length(cols_lev_c)
```

```{r fig.height=8, echo=FALSE}
table_q3 <- results %>%
  filter(`Q's` %in% c('Q8','Q9')) %>%
  select(`Q's`, matches('0=Not applicable_perc|1=Not at all_perc|2=Slightly_perc|3=Moderately_perc|4=Considerably_perc|5=Completely_perc')) %>%
  select(`Q's`,noquote(order(colnames(.))))

kable(table_q3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```
 
 # Visualization with Altair and Vega Light 

```{r include=FALSE}
data_temp <- temp[[17]]
names(data_temp)

cols_lev_a <- names(table(data_temp[,4]))
cols_lev_b <- 'No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'
cols_lev_c <- union(names(table(data_temp[,10])),names(table(data_temp[,11])))

```

```{r,  include=F}
# looking at the likert questions 4:8
data_list <- data_mung(df = data_temp,
  r1 = 4,
  r2 = 11)
```

```{r, include=F}
results_all <- do.call(bind_rows, data_list) 
names(results_all)
results <-  results_all %>%
  select(question,
         matches(paste0(cols_lev_a,'_perc' ,collapse="|")),
         matches(cols_lev_b),
         matches(paste0(cols_lev_c,'_perc' ,collapse="|"))) %>%
  mutate(`Q's` = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6','Q7', 'Q8'))
```

```{r, echo=FALSE}
table1 <- results %>%
  select(`Q's`, `survey item`=question)

kable(table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)


```

```{r include=F}
length(cols_lev_a)
```

```{r, echo=FALSE}
table_q1 <- results %>%
  filter(`Q's` == 'Q1') %>%
  select(`Q's`, matches('1=Not at all familiar_perc|2=A little familiar_perc|3=Moderately familiar_perc|4=Very familiar_perc|5=Extremely familiar')) %>%
  select(`Q's`,noquote(order(colnames(.))))  

kable(table_q1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = " % values are percents." )
```

```{r echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, echo=FALSE}
table_q2 <- results %>%
  filter(`Q's` %in% c('Q2', 'Q3', 'Q4','Q5','Q6')) %>%
  select(`Q's`,matches('No gains_perc|Small gains_perc|Medium gains_perc|Large gains_perc|Huge gains_perc'))

kable(table_q2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```

```{r fig.height=8, echo=FALSE}
table_q <- results %>%
  filter(`Q's` %in% c('Q7','Q8')) %>%
  select(`Q's`, `survey item`=question)

kable(table_q) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r include=F}
length(cols_lev_c)
```

```{r fig.height=8, echo=FALSE}
table_q3 <- results %>%
  filter(`Q's` %in% c('Q7','Q8')) %>%
  select(`Q's`, matches('0=Not applicable_perc|1=Not at all_perc|2=Slightly_perc|3=Moderately_perc|4=Considerably_perc|5=Completely_perc')) %>%
  select(`Q's`,noquote(order(colnames(.))))

kable(table_q3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
                footnote(general = "% Values are percents." )
```